Nonlinear system identification using machine learning tools

### 2021-04-20 sysID.tex
almost ready for group talk.:

\section{Large, CSTR and flash system example}
We next study the performance of the black-box NN modeling framework on a large chemical process that consists of a chemical reactor and flash separator in series. The process is depicted in Figure \ref{fig:cstr_flash}, and the ordinary differential equations (ODEs) with parameter values describing the plant model are shown in Appendix \ref{app:cstr_flash}. The model consists of 12 states ($H_r$, $C_{Ar}$, $C_{Br}$, $C_{Cr}$, $T_r$, $H_b$, $C_{Ab}$, $C_{Bb}$, $C_{Cb}$, $T_b$), 6 measurements ($H_r$, $C_{Br}$, $T_r$, $H_b$, $C_{Bb}$, $T_b$), and 2 control inputs ($F$, $D$). The sample time for the measurements is 1 min.

\begin{figure}[!h]
  \centering
  \includegraphics[page=1, height=0.5\textheight,
                   width=0.7\textwidth]{cstr_flash.pdf}
  \caption{Schematic of the CSTR and flash chemical process.}
  \label{fig:cstr_flash}
\end{figure}

\subsection{Model validation}

@@

\subsection{Steady state optimization}

\subsection{Dynamic economic optimization}

\section{Discussion}

>>>>

%\section{Large, CSTR and flash system example}
%We next study the performance of the black-box NN modeling framework on a 
%large chemical process that consists of a chemical reactor and flash separator 
%in series. The process is depicted in Figure \ref{fig:cstr_flash}, and the 
%ordinary differential equations (ODEs) with parameter values describing the 
%plant model are shown in Appendix \ref{app:cstr_flash}. The model consists of 
%12 states ($H_r$, $C_{Ar}$, $C_{Br}$, $C_{Cr}$, $T_r$, $H_b$, $C_{Ab}$, 
%$C_{Bb}$, $C_{Cb}$, $T_b$), 6 measurements ($H_r$, $C_{Br}$, $T_r$, $H_b$, 
%$C_{Bb}$, $T_b$), and 2 control inputs ($F$, $D$). The sample time for the 
%measurements is 1 min.

%\begin{figure}[!h]
%  \centering
%  \includegraphics[page=1, height=0.5\textheight,
%                   width=0.7\textwidth]{cstr_flash.pdf}
%  \caption{Schematic of the CSTR and flash chemical process.}
%  \label{fig:cstr_flash}
%\end{figure}

%\subsection{Model validation}

@@

%\subsection{Steady state optimization}

%\subsection{Dynamic economic optimization}

\section{Hybrid model}

\begin{equation*}
\begin{bmatrix}
\dfrac{dC_A}{dt} \\
\dfrac{dC_B}{dt} \\
\dfrac{dC_C}{dt}
\end{bmatrix} = \begin{bmatrix}
\dfrac{C_{Af} - C_A}{\tau} \\
- \dfrac{C_B}{\tau} \\
- \dfrac{C_C}{\tau}
\end{bmatrix} + f_N(C_A, C_B, C_C)
\end{equation*}

\section{Learn cost functions with input convex NNs}
Different proposal. NNs can be made convex from their inputs to outputs. 
Consider the following architecture (Amos, Xu, Kolter 2017) -

\begin{equation*}
	z_{i+1} = g_i(W_i^{z}z_{i} + W_i^{y}x + b_i), i=0, 1, ...k-1
\end{equation*}

If $g_i(\cdot)$ is convex and non-decreasing, $W_0^{z} = 0$, and $W_{1:k-1}^{z}$
are all non-negative, then the NN architecture is convex, i.e, the function 
$z_k(x)$ is convex.

\textbf{RTO algorithm}
\begin{itemize}
	\item Obtain steady-state data ($u_s$, $y_s$), and samples of the cost 
	curve ($\ell(u_s, y_s, p)$) based on current economic cost parameters.
	\item Fit the input convex NN to the cost curve and optimize.
\end{itemize}

Extensions - Can allow the NN to be non-convex in some inputs and convex in 
some inputs. So the NN cost function can be non-convex in economic 
parameters/disturbance estimates, but we will force it to be convex in $u_s$.
